PANCHANGE_analysis

### 2020-08-24 PANCHANGE_analysis.Rmd
model 0b disorders dummy coded

Model 0: Disorders
```{r}
model0 <- lm(
  formula = phq.diff_score_base_prepan ~ Disorder,
  data = dat)

>>>>

Model 0a: Disorders
```{r}
model0a <- lm(
  formula = phq.diff_score_base_prepan ~ Disorder,
  data = dat)

summary(model0a)
```

Model 0b: Disorders
```{r}
model0b <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    mhd.autism_aspergers_or_autistic_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat)

summary(model0b)
```
